A geometric approach to linear and quadratic Chabauty

### 2020-01-21 MS.tex
[Introduction] mentioned Dogra

Mention Flynn, Coleman, Kim, Balakrishnan et al. and their way of doing quadratic Chabauty

Say something about linear Chabauty geometric style

>>>>

Mention Flynn, Coleman, Kim, Balakrishnan, Dogra, and other mentionable people. and their way of doing (quadratic) Chabauty

Say something about linear Chabauty geometric style.
